---
title: "Question 1"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(readr)
library(readxl)
```

# Data

Just a brief description of the data used in this analysis.
There are 4 files which I am going to import to this file later, two for Kenya, two for Bangladesh.

For Kenya, there are "Kenya_Wealth", "Kenya_Income", and in each of them, it contains the following indicators:

- Gini coefficient
- Share of income/wealth held by highest 1%
- Share of income/wealth held by highest 10%
- Share of income/wealth held by bottom 50%
- Share of income/wealth held by middle 40%

The same applies for Bangladesh, with files "Bangladesh_Wealth" and "Bangladesh_Income". 

Note that the data for Banglandesh are imported in form of .xlsx files, as I 
found that it would be easier to import than the .csv file generated by the
website as csv files generated are not in regular format. And I have changed
the name for the files for convenience and clarity of the files.

```{r import-data, message=FALSE, warning=FALSE}
# !!! CHANGE THE WORKING DIRECTORY TO YOUR OWN DIRECTORY !!!
setwd("~/R/BI_Group_Proj/Data")

# Importing Kenya Data
Ken_W_Ineq <- read_delim("Kenya_Wealth_Inequality.csv", 
    delim = ";", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE, skip = 1)   # This is why I would rather use xlsx file

Ken_I_Ineq <- read_delim("Kenya_Income_Inequality.csv", 
    delim = ";", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE, skip = 1)

#Importing Bangladesh Data
Bang_W_Ineq <- read_excel("Bang_Wealth_Inequality.xlsx")
Bang_I_Ineq <- read_excel("Bang_Income_Inequality.xlsx")

```


# Comparing 



























